---
title: "Window Functions on Credit Index"
author: "Kevin Havis"
format: html
---

```{r}
#| output: false
library(tidyverse)
library(lubridate)
library(zoo)
```
## Introduction

Our data is the 2024 prices for a credit default swap index, a product that has surged in popularity in the last decade.

```{r}
# Read data
df <- read.csv('cdx_historical_data.csv')

glimpse(df)

```

```{r}
# Assign Date column to datetime

df <- df |> 
  mutate(Date = mdy(Date))

```

## Window Functions on Credit Index

Use window functions to calculate the year-to-date average and the six-day moving average for each of the metrics

```{r}
# Calculate year-to-date

df <- df |> 
  arrange(Date) |> 
  group_by(year = year(Date)) |> 
  mutate(across(-Date, cumsum, .names = "ytd_{.col}"))
```

```{r}
# Calculate rolling 6 day average

df <- df |> 
  arrange(Date) |> 
  mutate(across
         (c("Close.Last", "Volume", "Open", "High", "Low"),
           ~ rollapply(
             .x,
             width = 6,
             FUN = mean,
             fill = NA,
             partial = TRUE,
             align = 'right'),
           .names = "roll_mean_{.col}")
         )

```

## Visualize

Note sometimes the High and the Low averages diverge sharply, which usually reflects a intra-day announcement that significantly affected the market and in this case is "mellowed" by the rolling average. For a CDX, this is usually related to announcements or expectations on Federal rate changes.

```{r}
ggplot(df, aes(x = Date)) +
  geom_line(aes(y = roll_mean_High, color = "High")) +
  geom_line(aes(y = roll_mean_Low, color = "Low")) +
  labs(
    title = "6 Day Rolling Average of CDX.NA.IG",
    x = "Date",
    y = "6 Day Rolling Average",
    color = "Price"
  )

```

